% Chapter 7

\chapter{Conclusion} % Main chapter title

\label{Chapter7} % For referencing the chapter elsewhere, use \ref{Chapter6}

\lhead{Chapter 7. \emph{Conclusion}} % This is for the header on each page - perhaps a shortened title

%----------------------------------------------------------------------------------------

The past six months of my internship have been very instructive for me. It's the first time that I participated in an industrial research project. This opportunity allows me to learn and develop myself in many areas. I gained a lot of experience, especially in CWMP and Z-Wave Protocol. A lot of activities are familiar with what I have learned at school. They enhanced my competence in computer science and inspired my interests in industrial research work.

On the other hand, I also encountered problems that I had never come across before. It was good to find out what my weaknesses are. This helped me to define which skills and knowledges I have to improve in the coming study time.

One thing I appreciate a lot is the DM2E meeting organized by group members. They invite researchers specialized in one particular area to share their opinions and ideas with other people. Even if I didn't understand all discussions, I did get a global picture for my unknown topics from these presentations. Such experience makes me eager to learn more and explore more; it really broadened my horizons.

From this internship I also learned the importance of time management. Once I realized what I had to do, I organized my day and work so that I did not waste my hours. A Gantt diagram of my internship helps with the time management.

This six-month internship passed too quickly. I am grateful for meeting so many wonderful staff members. I will try my best to apply all I learned here into my future careers and sincerely give all my best regards to my group members.
